\textbf{Access Control for Content Distribution Network Assets}

### 2016-06-01 tex/paper.tex
Changed implementation background and abstract

%}}}
\begin{abstract}
This work presents a technique for implementing Copy-on-Write on top of an unaware persistent
storage. The system in this case is a security management system, but the technique and conclusions
drawn are general enough to be applicable to any system with vaguely similar consistency
requirements. The scalability of the storage system is tested and the technique is evaluated. The
technique is shown to be quite efficient (scalable to >6.000 simultaneous active users per node),
but a better solution is also suggested in the conclusion.\\

@@

\subsubsection{The current system} \label{sec:current_system}
Today a system called Battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use of the
security features that the CDNs are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

In the current system you can only upload a file once as there will be a collision in the upload
otherwise, as the old and the new file will have the same MD5 hash, which is by design as duplicate
content just wastes space on the CDN. The problem with this is that the current interface does not
handle it very well as one file can not be shown or uploaded in two different places in 
Battlebinary's virtual filesystem.

>>>>

%}}}
\begin{abstract}
This work presents a technique for implementing Copy-on-Write on top of a persistent storage. The
method was developed from the needs of a security management system, but the technique and
conclusions drawn are general enough to be applicable to any system with vaguely similar consistency
requirements. The scalability of the security management system is tested and the technique is
evaluated with load testing and model checking. The implementation is shown to be scalable for up to
>6.000 simultaneous active users per node, but based on our experience a better solution is 
suggested in the conclusion.\\

@@

\subsubsection{The current system} \label{sec:current_system}
Today a system called Battlebinary~\cite{BATTLEBINARY} is used by Uprise for managing and uploading
files, mostly images, to content delivery networks. The current system does not make use of the
security features that the CDNs are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is available to the public, but since its identifier is composed out
of its original filename concatenated with a part of the MD5 hash of the content of the file. This
makes it a very computationally heavy process to access the file on the CDN without access to the
original file or a reference to the URI, as the identifier would have to be brute forced.

In the current system you can only upload a file once, since there will be an identifier collision.
This is due to the old and the new file having the same MD5 hash, which is by design as duplicate
content just wastes space on the CDN. The problem with this is that the current interface does not
handle it very well, since one file can not be shown or uploaded in two different places in
Battlebinary's virtual filesystem.
